\documentclass[11pt,letterpaper]{article}
\usepackage{fancyhdr,lastpage,metre}
\usepackage[]{titlesec}

\pagestyle{fancy}

\setlength{\pdfpageheight}{11in}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0.5in}
\setlength{\headsep}{0.25in}
\setlength{\textheight}{8in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0pt}
\setlength{\headwidth}{6.5in}

\lhead{\textit{Travel Support for SenSys 2010}}
\rhead{\textit{G. Challen}}
\cfoot{\textit{\thepage~of~\pageref{LastPage}}}
\renewcommand{\headrulewidth}{0.25pt}
\renewcommand{\footrulewidth}{0.25pt}

\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}}

\begin{document}

\begin{center}
{\huge \textbf{Geoffrey Challen}}\\
{\Large n\'{e} Werner-Allen}
\end{center}
Department of Computer Science and Engineering\\
University at Buffalo\\
201 Bell Hall\\
Buffalo, NY 14260-2000\\
\href{mailto:challen@buffalo.edu}{\texttt{challen@buffalo.edu}}\\
\url{http://www.cse.buffalo.edu/~challen/}

\section*{Professional Preparation}
Harvard University, Physics, A.B. 2003\\
Harvard University, Computer Science, Ph.D. 2010\\
Massachusetts Institute of Technology, Post-Doctoral Researcher, 2010-2011

\section*{Appointments}
Starting Fall 2011, Assistant Professor, SUNY Buffalo

\section*{Related Publications}

\begin{list}{\labelitemi}{\leftmargin=1em}

\item \textbf{Mercury: A Wearable Sensor Network Platform for High-Fidelity
Motion Analysis}\\
Konrad Lorincz, Bor-rong Chen, Geoffrey Werner Challen, Atanu Roy Chowdhury,
Shyamal Patel, Paolo Bonato and Matt Welsh. In Proceedings of the 7th ACM
Conference on Embedded Networked Sensor Systems (SenSys'09).

\item \textbf{Lance: Optimizing High-Resolution Data Collection in Wireless
Sensor Networks}\\
Geoffrey Werner-Allen, Stephen Dawson-Haggerty and Matt Welsh. In Proceedings
of the 6th ACM Conference on Embedded Networked Sensor Systems (SenSys'08).

\item \textbf{Resource Aware Programming in the Pixie OS}\\
Konrad Lorincz, Bor-rong Chen, Jason Waterman, Geoffrey Werner-Allen and Matt
Welsh. In Proceedings of the 6th ACM Conference on Embedded Networked
Sensor Systems (SenSys'08).

\item \textbf{Firefly-Inspired Sensor Network Synchronicity with Realistic
Radio Effects}\\
Geoffrey Werner-Allen, Geetika Tewari, Ankit Patel, Radhika Nagpal and Matt
Welsh. In Proceedings of the 3rd ACM Conference on Embedded Networked Sensor
Systems (Sensys'05).

\item \textbf{Simulating the Power Consumption of Large-Scale Sensor Network
Applications}\\
Victor Shnayder, Mark Hempstead, Bor-rong Chen, Geoffrey Werner-Allen, and
Matt Welsh. In Proceedings of the 2nd ACM Conference on Embedded Networked
Sensor Systems (SenSys'04).

\end{list}

\section*{Other Significant Publications}

\begin{list}{\labelitemi}{\leftmargin=1em}

\item \textbf{IDEA: Integrated Distributed Energy Awareness for Wireless
Sensor Networks}\\
Geoffrey Werner Challen, Jason Waterman and Matt Welsh. In Proceedings of the
8th Annual International Conference on Mobile Systems, Applications and
Services (MobiSys'10).

\item \textbf{Peloton: Coordinated Resource Management for Sensor Networks}\\
Jason Waterman, Geoffrey Werner Challen, and Matt Welsh. In Proceedings of
the 12th Workshop on Hot Topics in Operating Systems (HotOS'09).

\item \textbf{Fidelity and Yield in a Volcano Monitoring Sensor Network}\\
Geoffrey Werner-Allen, Konrad Lorincz, Jeff Johnson, Jonathan Lees and Matt
Welsh. In Proceedings of the Seventh USENIX Symposium on Operating Systems
Design and Implementation (OSDI'06).

\item \textbf{MoteLab: A Wireless Sensor Network Testbed}
Geoffrey Werner-Allen, Pat Swieskowski, and Matt Welsh. In Proceedings of the
Fourth International Conference on Information Processing in Sensor Networks
(IPSN'05), Special Track on Platform Tools and Design Methods for Network
Embedded Sensors (SPOTS).

\end{list}

\section*{Synergistic Activities}

\begin{list}{\labelitemi}{\leftmargin=1em}

\item Program Committee Member, 31st IEEE Real-Time Systems Symposium (RTSS
2011) (Wireless Network Systems Track), Ninth Annual IEEE International
Conference on Pervasive Computing and Communications (PerCom 2011)
(Work-in-Progress Session).

\item 2009-2010 Siebel Scholar.

\item Recipient of the 2005 Harvard Division of Engineering and Applied
Sciences Teaching Fellow Award.

\end{list}

\textbf{Ph.D. Thesis Advisor:} Matt Welsh (Harvard University)

\vspace{0.10in}

\textbf{Post-Doctoral Supervisor:} Hari Balakrishnan (Massachusetts Institute
of Technology)

\vspace{0.10in}

\textbf{Collaborators:} Mike Allen (Coventry University), Paolo Bonato
(Spaulding Rehabilitation Hospital), James Brusey (Coventry University),
Bor-rong Chen (Harvard University), Stephen Dawson-Haggerty (UC Berkeley),
Elena Gaura (Coventry University), Lewis Girod (Massachusetts Institute of
Technology), Atanu Roy Chowdhury (Blue Highway), Konrad Lorincz (BBN
Technologies), Shyamal Patel (Spaulding Rehabilitation Hospital), Jason
Waterman (Harvard University).

\vspace{0.10in}

\textbf{Former Ph.D. Students:} None.

\end{document}
