\documentclass[11pt,letterpaper]{article}
\usepackage{fancyhdr,lastpage,metre}
\usepackage[compact]{titlesec}

\pagestyle{fancy}

\setlength{\pdfpageheight}{11in}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0.5in}
\setlength{\headsep}{0.25in}
\setlength{\textheight}{8in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{10pt}
\setlength{\headwidth}{6.5in}

\lhead{\textit{Travel Support for SenSys 2010}}
\rhead{\textit{G. Challen}}
\cfoot{}
\renewcommand{\headrulewidth}{0.25pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|ccc|c|}
\hline
& \textbf{Airfare} & \textbf{Lodging} & \textbf{Registration} & \textbf{Total} \\
\hline \hline
1 Attendee & \$750 & \$300 & \$250 & \$1300 \\
16 Attendees & \$12,000 & \$4,800 & \$4,000 & \$20,800 \\
\hline
\end{tabular}
\end{center}
\caption{Budget summary. Items are explained below.}
\label{table-budget}
\end{table}

\section*{Budget Justification}
\label{sec-budget}

Given the conference location we are requesting \$20,800 to support SenSys'10
travel grants supporting 16 applicants. Table~\ref{table-budget} details the
costs involved. Airfare is estimated based on round-trip travel from the East
and West Coasts. Lodging is based on numbers for hotels near ETH Zurich
campus --- the SenSys'10 conference site --- assuming double occupancy;
applicants will be expected to arrange to share rooms. SenSys'10 registration
costs have not yet been set so \$250 is estimated based on SenSys'09 student
registration costs (\$380) and a 2009 budget surplus which is expected to
reduce student registration costs further this year.

Note that it is expected that the amounts awarded will not completely offset
the total cost of attendance, as airport transportation, incidental meals and
other miscellaneous expenses are not included. This is intentional. Selected
applicants will be expected to contribute a reasonable amount of their own
financial resources towards the intellectual growth and professional
advancement SenSys'10 will facilitate.

Our request is higher than the amount requested for SenSys'09 (\$20,800
v.~\$15,000 in 2009) and supports fewer applicants (16 v.~20 in 2009) due to
the higher costs of international travel. SenSys'07, held in Sydney,
Australia, awarded 14 grants and a total of \$26,400 and provides another
baseline for comparison.

\end{document}
